Neighbor-Based Decentralized Training Strategies for Multi-Agent Reinforcement Learning

### 2024-10-12 paper-2024-sac-marl-neighbouring-strategies.tex
fix experimental setup

We ran a total of $35$ training experiments, 
namely: $5$ different methods %% TODO check how many ex are discussed
  (centralized, distributed and the three neighbor strategies discussed).
Each method was evaluated across 10 distinct random seeds to enhance the statistical robustness of the observed results.
%
Each experiment consisted of $50$ training episodes. 
%
Furthermore, we ran $15$ evaluation experiments, namely: $5$ different methods and for each method 
  we varied the number of agents ($8$, $16$ and $32$) to assess the metrics under various conditions.
  In this case, for each experiment we ran $100$ evaluation episodes.

>>>>

We ran a total of $42$ training experiments, 
namely: $6$ different methods %% TODO check how many ex are discussed
  (centralized, distributed and the three neighbor-based strategies discussed).
Each method was evaluated across 10 distinct random seeds to enhance the statistical robustness of the observed results.
%
Each experiment consisted of $50$ training episodes. 
%
Furthermore, we ran $15$ evaluation experiments, namely: $5$ different methods and for each method 
  we varied the number of agents ($8$, $16$ and $32$) to assess the metrics under various conditions.
  In this case, for each experiment we ran $100$ evaluation episodes.
